Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-06 Codes/PrepareResults.rmd
ctree added to manuscript

>>>>

```{r}
# /*=================================================*/
#' # Sample CT figure (cach)
# /*=================================================*/

library(causalTree)
library(here)
library(rpart)
library(rattle)

data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
  na.omit() %>%
  dplyr::rename(tgtn = NPlan, tgts = SRPlan)

data_dt <- data.table(data_sf) %>%
  setnames(names(.), tolower(names(.)))

tgts_ls <- data_dt[, tgts] %>%
  unique() %>%
  sort()

ctree_data <- copy(data_dt) %>%
  .[tgts %in% tgts_ls[1:2], ] %>%
  .[, treat := ifelse(tgts == tgts_ls[2], 1, 0)] %>%
  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
  .[, yield := yield * 62.77]

tree <- causalTree(
  yield ~ slope + ecs,
  data = ctree_data,
  treatment = ctree_data$treat,
  split.Rule = "CT",
  cv.option = "CT",
  split.Honest = T,
  cv.Honest = T,
  split.Bucket = F,
  xval = 5,
  cp = 0,
  minsize = 20,
  propensity = 0.5
)

opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
opfit <- prune(tree, opcp)
```

### 2022-02-06 Writing/manuscript_cea.rmd
ctree added to manuscript

```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
# knitr::include_graphics("./GitControlled/Writing/ctree_ex.pdf")
readPNG(here("GitControlled/Writing/ctree_ex.png")) %>% grid.raster()
```

>>>>

```{r ct-ex, fig.width=4, fig.height=4, fig.align="center", fig.cap = "An illustrative example of causal tree"}
fancyRpartPlot(opfit, sub = "")
```
